REACT-SCOT analysis script report

### 2020-07-03 casecontrol_script.Rmd

knitr::kable(with(cc.all[cc.all$CASE==1, ],
                  paste.colpercent(table(deathwithin28, unitcategory))), 
             escape=FALSE, 
             booktabs=TRUE,
             row.names=FALSE,
             caption="Death within 28 days by hospitalization group") %>%
    kable_styling(latex_options="hold_position")

@@

knitr::kable(table(cc.all$CASE, cc.all$group, exclude=NULL),
             escape=FALSE, 
             booktabs=TRUE,
             row.names=FALSE,
             caption="Case groups") %>%
    kable_styling(latex_options="hold_position")

@@

```{r NRS.cases, echo=FALSE, warning=FALSE, message=FALSE}

knitr::kable(with(subset(cc.all, CASE==1 & nrs_covid_case==0), table(criticalcare, deathwithin28, exclude=NULL)),
             caption="CASE x NRS COVID case")

knitr::kable(with(subset(cc.all, CASE==1), table(criticalcare, nrs_covid_case, exclude=NULL)),
             caption="Critical care x NRS COVID case")

knitr::kable(with(subset(cc.all, CASE==1), table(nrs_covid_case, deathwithin28, exclude=NULL)),
             caption="NRS covid case x death within 28 days")

>>>>

knitr::kable(with(cc.all[cc.all$CASE==1, ],
                  paste.colpercent(table(deathwithin28, casegroup))), 
             escape=FALSE, 
             booktabs=TRUE,
             row.names=FALSE,
             caption="Death within 28 days by case group") %>%
    kable_styling(latex_options="hold_position")

@@

knitr::kable(table(cc.all$CASE, cc.all$casegroup, exclude=NULL),
             escape=FALSE, 
             booktabs=TRUE,
             row.names=FALSE,
             caption="Case groups") %>%
    kable_styling(latex_options="hold_position")

@@

```{r criticalcare, echo=FALSE, warning=FALSE, message=FALSE}

knitr::kable(with(subset(cc.all, CASE==1), table(criticalcare, deathwithin28, exclude=NULL)),
             caption="critical care x deathwithin28")
